Fast Hyper-Parameter Selection for Graph Kernels via Subsampling and Multiple Kernel Learning

### 2016-11-25 paper.tex
Modified dataset description

\section{Experimental Assessment}
We conducted our experiments on five real-world datasets (see \cite{DaSanMartino2016} for a more detailed description).
%AIDS~\cite{Weislow1989a}, CAS\footnote{http://cheminformatics.org/datasets/bursi/},
%CPDB~\cite{Helma2004a}, NCI1~\cite{Wale2006} and GDD~\cite{dobson2003}.
%The first four datasets contain chemical particles encoded in graph form, while the latter encodes proteins.
All the nodes are labelled and there are no self loops.
The AIDS dataset contains 1503 chemical compounds (encoded in graph form), labelled according to
their antiviral activity; CAS and CPDB store 4337 and 684 mutagenic
compounds respectively; NCI1 consists of 4110 chemical compounds screened for activity against 
non-small lung cancer cells; GDD is composed of 1178 X-ray crystal structures of
proteins.
All the datsets represent binary classification problems.

Firstly, we performed some experiments to check how many samples are required to make $\boldsymbol{\eta}$ and $\hat{\boldsymbol{\eta}}$ similar.
In our context two weights vectors are similar if they provide the same top kernels. By the way the metric used for comparison is the jaccard similarity score. \figurename\ \ref{fig:jaccard} show the jaccard score between the indices of top kernels selected using $\boldsymbol{\eta}$ and $\hat{\boldsymbol{\eta}}$ with different threshold and different subsampling dimension.
According to other preliminary results, we fix the dimension of subset used in the first step to learn $\hat{\boldsymbol{\eta}}$ as 10\% and the number of top kernels as 10\%.

>>>>

\section{Experimental Assessment}
We conducted our experiments on five real-world datasets (see \cite{DaSanMartino2016} for a more detailed description).
%AIDS~\cite{Weislow1989a}, CAS\footnote{http://cheminformatics.org/datasets/bursi/},
%CPDB~\cite{Helma2004a}, NCI1~\cite{Wale2006} and GDD~\cite{dobson2003}.
%The first four datasets contain chemical particles encoded in graph form, while the latter encodes proteins.
All the nodes are labeled and there are no self loops.
The AIDS dataset contains chemical compounds (encoded in graph form), labeled according to
their antiviral activity; CAS and CPDB store compounds labeled according to their mutagenicity; NCI1 consists of chemical compounds screened for activity against non-small lung cancer cells; GDD is composed of X-ray crystal structures of
proteins.
All the datasets represent binary classification problems.

Firstly, we performed some experiments to check how many samples are required to make $\boldsymbol{\eta}$ and $\hat{\boldsymbol{\eta}}$ similar.
In our context two weights vectors are similar if they provide the same top kernels. By the way the metric used for comparison is the jaccard similarity score. \figurename\ \ref{fig:jaccard} show the Jaccard score between the indices of top kernels selected using $\boldsymbol{\eta}$ and $\hat{\boldsymbol{\eta}}$ with different threshold and different subsampling dimension.
According to other preliminary results, we fix the dimension of subset used in the first step to learn $\hat{\boldsymbol{\eta}}$ as 10\% and the number of top kernels as 10\%.
